Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-12-18 demystify.tex
updates

@@

On average, I spend about 10--15 minutes reviewing each application (less for clear rejections and more for potential acceptances). While this seems short, it is not that difficult to tell if an application is good or bad.  In fact, this
is twice what other faculty spend on average, e.g., Philip Guo spent \href{https://pg.ucsd.edu/PhD-application-tips.htm}{3--5 minutes} per application.

@@

Do not include ranking (e.g., Assistant, Associate, Scientist, ...) when referring to someone. I see many international students include a lengthy title of people they know, e.g., \emph{I am advised by Asst. Prof. X, and I also collaborate with Distinguished Scientist Y}.  This is \emph{not necessary} and makes it look like you're trying to show off your connections. These nuances represent some cultural differences that you may encounter and will gradually adapt to. More on cultural differences in \autoref{sec:cultural}.

@@

\paragraph{School \autoref{chap:your-school}} Adcom already knows about your school, which is a plus (see \autoref{chap:your-school}). You are also more familiar with the US education system and culture (so hopefully you are aware of the cultural issues listed in \autoref{sec:cultural}).

@@

\chapter{Cultural Differences}\label{sec:cultural}

@@

This section lists some general cultural issues that students, especially international ones, might want to pay attention to.

>>>>

\epigraph{Bart: ``Are we there yet? Are we there yet? Are we there yet?''\\
Homer: ``No!''\\
Bart: ``Okay, how about now?''}{\textsc{The Simpsons}}

@@

In most schools I've been at, the application deadline is in December, and adcom meets begins when school starts in mid or end of January. Adcom chair sends out review assignments to adcom members, about 30ish per faculty (\autoref{sec:adcom}). We usually have about 2 weeks to review all applications. As mentioned in~\autoref{sec:adcom-discuss}, adcom members review applications individually and independently. We only discuss when there are disagreements (adcom chair will determine which applications to discuss).

I typically reserve a whole day to review all applications (this is to be fair to all applicants).
On average, I spend about 10--15 minutes reviewing each application (less for clear rejections and more for potential acceptances). While this seems short, it is not that difficult to tell if an application is good or bad.  In fact, this
is twice what other faculty spend on average, e.g., Philip Guo spent \href{https://pg.ucsd.edu/PhD-application-tips.htm}{3--5 minutes} per application.

@@

Do not include ranking (e.g., Assistant, Associate, Scientist, ...) when referring to someone. I see many international students include a lengthy title of people they know, e.g., \emph{I am advised by Asst. Prof. X, and I also collaborate with Distinguished Scientist Y}.  This is \emph{not necessary} and makes it look like you're trying to show off your connections. These nuances represent some cultural and academic differences that you may encounter and will gradually adapt to. More on cultural differences in \autoref{sec:cultural}.

@@

\paragraph{School \autoref{chap:your-school}} Adcom already knows about your school, which is a plus (see \autoref{chap:your-school}). You are also more familiar with the US education system and academic culture (\autoref{sec:cultural}).

@@

\chapter{Academic and Cultural Differences}\label{sec:cultural}

@@

This section lists some general academic and cultural issues that students, especially international ones, might want to pay attention to.
